---
title: "Architecture"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{architecture}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval=FALSE
)
```


```{r, message=FALSE, eval=FALSE}
library(tidyverse)
library(Momocs2)
```

Let's have a drink^[Please drink responsibly]. Do you prefer beer or wine?

```{r, results='hold'}
mosaic(bot, type) # add id support
```

## Everything is a tibble

You see the visual representation of a "mom" object that looks like this: 

```{r}
bot                  # shipped with Momocs2
```

Across MomX, the main object is `mom`, are [tibbles](https://tibble.tidyverse.org/), slightly augmented for morphometrics. Tibbles themselves are built on top of goold old `data.frame`.

Keep this in mind:

> A mom is a tibble, a tibble is a data.frame, a data.frame is a list, and a list can contain anything, including other lists.

Typically, at some point of the MomX pipeline, one or more columns in these tibbles will store coordinates (`<coo_list>`), coefficients (`<coe_list>`), etc.

## `coo`rdinates classes

The `coo` column above is a `<coo_list>` a list of single shapes. Let's have a look:

```{r}
bot$coo %>% head(2)
```

Each single shapes are stored in tibbles with exactly 2 columns, named `x` and `y`. Such a thing is a `<coo_single>`.

In morphometrics, shapes rarely come single but as collection of shapes, hence the `<coo_list>`. Also, they usually have covariates attached that should be firmly tied to it, hence the `<mom_tbl>`.

## `coe`fficients classes
In morphometrics, the destiny of coordinates is to be turned into coefficients. Coefficients are obtained using morphometric methods like elliptical Fourier transforms, or Procrustes alignment.

```{r}
efourier(bot$coo[[1]])
```

Here an elliptical Fourier tranform turned a `<coo_single>` into a `<coe_single>`. They are tibbles with exactly 1 row but with possiby many columns.

Morphometrics is pivotationnal, or transpositionnal, in nature: it turns long tables (many rows, few columns) into large table (1 row, many columns)

Yes, `<coe_single>` can be gathered into `<coe_list>`, and can be a column in a `<mom>`.

Now you know how it works.

The best news is that, in most cases, and whether you have met retired Momocs before, you won't have to bother with this^[I did it for you ;-)]:

```{r}
bot %>% efourier()
```

## MomX and the tidyverse

MomX owes everything to the tidyverse and to the humans behind it. I deeply believe, it is not a trend or something, it is more the right way to do things in data science as a whole.

In particular, MomX :

* is built on top of the tidyverse. For example, Momocs2 has no other dependencies outside those that the tidyverse also uses
* embraces the [tidy tools manifesto](https://cran.r-project.org/web/packages/tidyverse/vignettes/manifesto.html)
* is directly inspired, in its ecosystemic nature, by the tidyverse

MomX thus makes a massive use of `dplyr`, `ggplot2`, `purrr` and, on a lighter note, on `magrittr` pipe operators. They are a must and you haven't heard of these, stop what you're doing, close the door and go there :

> https://r4ds.had.co.nz/

