---
title: "Momocs2_intro"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Momocs2_intro}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(Momocs2)
```

Momocs2 is a rewrite of Momocs. The main changes are:

* Momocs2 now only deals with core morphometrics operations: typically coo manipulation and morphometrics methods that turn them into coe.
* Importing methods are in Momit, stat methods in Momstats. More generally see MomX. This is a much easier way for me to maintain packages and develop more.
* Coo and Coe classes are now tibble, in other words tidyverse-ready
* Restrictions are alleviated so that additional methods should be easier to add.
* All graphics are ggplot2
* You're not bound to Momocs: you can come, use some of it and return to your preferred environment 😄

# coo functions

 * coo_modifyers modify the shapes: return coo_single on coo_single, modify on place coo columns for coo_tbl
 * coo_descriptors describe the shape: return value on coo_single, create new columns on coo_tbl.

You can pass single shapes or list of shapes to all `coo_*` methods. You're not bound to Momocs, you can come, use it and return to your preferred environment.

example here

### Architecture: design and classes

 * Momocs handles shapes that are (or can be turned into) [tibbles](https://tibble.tidyverse.org/). So basically anything with two columns is fine. They are called **coo_single**. They can be collated into **coo_list**, which in turn can be part of a tibble, as a list column. Such tibble have a dedicated class: **coo_tbl**
 * All morphometric methods turn shapes into coefficients. `coo_single`, `coo_list` and `coo_table` are turned into `coe_single`, `coe_list` and `coe_tbl`. `coe_single` have a single row but can have many columns that are morphometrics variables.







