---
title: "Shape manipulation"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{shape}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Momocs2 shape manipulation functions come in two different flavours, those which: 

* _modify_ shapes start with `coo_`: eg `coo_center` and `coo_sample`, 
* _describe_ shapes start with `get_`: eg `get_centsize` and `get_area`,  

We could add morphometrics operation in the second category fo shape descriptors, but we will not.

If you want an exhaustive list you can :

* type `coo_` and then press `<tab>` and let autocompletion do its job
* have a look to the [Reference section](https://momx.github.io/Momocs2/reference) of the website

## Implementation
Each `coo_` function, is actually a _method_, that is a function that will do a different job depending on the class it is pass with. That mechanism is what allows the following to work:

```{r, eval=FALSE}
coo_center(bot)           # a mom_tbl
coo_center(bot$coo)       # a coo_list
coo_center(bot$coo[[1]])  # a coo_single
```

Besides arguments that a particular `coo_`, eg `coo_trans` may have, these three methods apply seamlessly using the same grammar. 

Typically, code is defined for the `coo_single` method; for `coo_list` it is applied using `purrr::map`; for `mom_tbl` it is slightly more subtle. Indeed, all `coo_*` methods on `mom_tbl` also have `from_col` and `to_col` arguments. This allows to work using different columns and creating columns with the name you want. By default, `coo` is used for both `from_col` and `to_col` so this:

```{r, eval=FALSE}
coo_center(bot)
```

is actually a shortcut for:

```{r, eval=FALSE}
coo_center(bot, from_col=coo, to_col=coo)
```

This is useless if you have a single column with coordinates named `coo` and if you want the new `coo` to be the centered (or anything-ed) version of it. Which is typically the behaviour you want. But this will greatly simplify more complex manipulations.




* coo_foo.default implements the modification
* coo_foo.list allows is use on coo_list with `purrr::map*`
* coo_foo.coo_tbl allows its use on `coo_tbl` _and_ to specify from and to columns, using [tidyevaluation](https://tidyeval.tidyverse.org/)
