---
title: "Survival"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{survival}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval=FALSE
)
```

As mom objects are tibbles, they probably look more than familiar to you. And as they are tibbles, the entire tidyverse comes for free. 

This vignette illustrates how to use the most common tidyverse functions for the most common data manipulation tasks in MomX. Things shown here will "work" on any `data.frame` and can be found easily from the tidyverse homepage: [https://www.tidyverse.org/]().

## The pipe operators 
First thing first: if you're not familiar with these `%>%` everywhere in my code, examples, etc. let me just show you some "base R":

```{r, eval=FALSE}
bot_c    <- coo_center(bot)
bot_cs   <- coo_scale(bot_c)
bot_csa  <- coo_align(bot_cs)
bot_csa1 <- coo_slidedirection(bot_csa)
bot_eft  <- efourier(bot_csa1)
```

And now some "piped R":
```{r, eval=FALSE}
bot %>% 
  coo_center %>% 
  coo_scale %>% 
  coo_align %>% 
  coo_slidedirection("right") %>% 
  efourier()
```

Unless you're an ultra-rthodox or something^[And if you're a post-modeRnist you will appreciate the [nakedpipe](https://github.com/moodymudskipper/nakedpipe) too], you will likely vote for the second one. We should not reduce the pipe-operator to a matter of taste, it is also:

* safer (it reduces typos)
* easier and more comfy to read (thus to understand and debug)
* easier and faster to write (use RStudio shortcut!)
* a guarantee that functions consistently use data as first argument

> Read the [_Introduction to magrittr_](https://magrittr.tidyverse.org/articles/magrittr.html)

## `dplyr`: common data manipulation

> If you're not familiar with dplyr, the [_Introduction to dplyr_](https://cran.r-project.org/web/packages/dplyr/vignettes/dplyr.html) will definitely change your life.

By our side, we will play with olive stones:

```{r, message=FALSE, eval=FALSE}
library(tidyverse)
library(Momocs2)
olea
```

### Filtering
You can filter individuals based on logical conditions:

```{r, eval=FALSE}
olea %>% filter(view == "VL")
```

And you can group conditions:

```{r}
olea %>% filter(view == "VL", var != "Aglan", ind %in% c("O10", "O11"))
```

## Select rows

Except in "inspection" case, it's generally not perfectly safe to subset positionnally but that's the job of `slice`

```{r}
olea %>% slice(1:5)

olea %>% slice(-(1:5))

```
